### 2021-11-08 sections/data_presel.tex
small typos

The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirement are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identificaiton so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
\end{itemize}

The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger.
The two $\had$ candidates are required to have charges of opposite sign.

>>>>

The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identificaiton so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
\end{itemize}

The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:
\begin{itemize}
\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-tagged jet.
\end{itemize}
